### 2023-11-24 tree_hackathon.Rmd
Update tree_hackathon.Rmd

1. Feed the list of elements (in our case element 9, 2)
2. Feed the boundary ages (1 - 0.2)
3. Have a function to detect the subtree with the element

    a.

tree$edge
[1,] 1 1
tree$nodelabel
"d"

    b. go back to the orginal tree
    c. find the sub tree(s) that go into the future
    d. cut these sub trees(s) at the younger age (use `slice.tree`)

>>>>

1. Feed the list of elements (in our case element 9, 2)
2. Feed the boundary ages (1 - 0.2)
    * Edit the age boundaries to that the old age becomes the root of the tree and the young age becomes the cutting point
3. Recreate the subtree spanning from the selected elements (descendant from them)
    * Make sure that the elements names are kept
4. Using `slice.tree` to cut the upper boundary (young age)
5. Return the new subtree
